The population of long-period exoplanets --- \\ Fully-automated discovery \& characterization of long-period transiting exoplanet candidates in the \kepler\ archive \vspace{-3\baselineskip}

### 2016-07-02 document/ms.tex
words about the catalog of candidates

Applying the search procedure described in \sect{search} to the \kepler\ light
curves of the targets selected in \sect{target-selection}, we find 16
convincing transit candidates.
Visual inspection of each candidate confirms the reliability of the
classification and no candidates are manually removed from the catalog.
Of these, three candidates have two transits in the \kepler\ baseline and the
remainder have only one observable transit.
The candidates and their inferred physical parameters are listed in
Table~\ref{tab:catalog} and the light curves are plotted in
\dfmfig{light-curves}.

@@

\section{Astrophysical false positives}

>>>>

Applying the search procedure described in \sect{search} to the \kepler\ light
curves of the 39,036 targets selected in \sect{target-selection}, we find 16
convincing transit candidates.
Visual inspection of each candidate confirms the reliability of the
classification and no candidates are manually removed from the catalog.
Of these, three candidates have two transits in the \kepler\ baseline and the
remainder have only one observable transit.
The candidates and their inferred physical parameters are listed in
Table~\ref{tab:catalog} and the light curves are plotted in
\dfmfig{light-curves}.

Two of the shortest period candidates~--~both with two observed
transits~--~have previously been studied in detail \citep[KIC~8800954 and
KIC~3239945;][]{Kipping:2014a, Kipping:2016}.
Table~\ref{tab:catalog} indicates the candidates that were also discovered by
earlier searches for long-period transiting systems using visual inspection
\citep{Wang:2015, Uehara:2016}.
The consistency between our results and the earlier catalogs is reassuring.
Our automated search did not find any more candidates than visual inspection
of the light curves of known KOIs \citep{Uehara:2016} and one candidate
(KIC~3230491) reported by the human analysis was discarded as grazing by our
search.
The PH citizen science project reported five long-period candidates with one
or two observed transits in our target list \citep{Wang:2015}.
Of these, we also find two (KIC~8410697 and KIC~10842718) although we find a
second transit in the KIC~8410697 system that was not previously reported.
The three other candidates reported by \citet{Wang:2015} that we miss
(KIC~5536555, KIC~9662267, and KIC~12454613) are have low signal-to-noise
transits that do not pass our initial signal-to-noise threshold.
Six of the candidates in Table~\ref{tab:catalog} have not been previously
published.

The candidate in the light curve of KIC~4754460 as an individual transit
candidate but another deeper eclipse can be found at a KBJD of 1587.13; right
at the beginning of Quarter 17.
This eclipse was missed by the automated search because only the second half
of the eclipse is observed.
The most likely explanation of this system is that the listed candidate is the
secondary eclipse of a binary system but we will keep the candidate is the
list and treat this effect statistically in \sect{false-positives}.

@@

\section{Astrophysical false positives}\sectlabel{false-positives}
